---
title: "Assignment-2-Joey"
output: html_document
---

<<<<<<< HEAD
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
This is about an investigation of which country's wine is generallly better. This is about an investigation of which country's wine is generallly better. This is about an investigation of which country's wine is generallly better. This is about an investigation of which country's wine is generallly better. This is about an investigation of which country's wine is generallly better. 

## Table

## Graph

## Conclusion
|Marks                     |1-10 |
|--------------------------|:---:|
| Overall effort           |     | 
| Clear commits            |     | 
| Created 2 branches       |     |  
| Merged 2 branches        |     |
| 2 Graphs with captions   |     |
| 2 Graphs referenced      |     |
| 2 Tables with captions   |     |
| 2 Tables refrenced       |     |
| Overall report quality   |     |

=======

```{r pressure, echo=FALSE}
plot(pressure)
```
>>>>>>> graph

